---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Raphael John (12548296), Fabian Walthes (12564674)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.

## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  Start by initializing a new R project with git support, called
    `2024-exeRcise-sheet-3`. If you forgot how to do this, you can
    follow this
    [guide](https://malikaihle.github.io/Introduction-RStudio-Git-GitHub/rstudio_project.html).
b)  Commit the files generated by Rstudio.
c)  For all of the following tasks in this exercise sheet we ask you to
    always commit your changes after finishing each subtask e.g. create
    a commit after task *1d*, *1e* etc.

> Note: This applies only to answers that have text or code as their
> answer. If you complete tasks in a different order or forget to commit
> one, this is no problem. If you change your answers you can just
> create multiple commits to track the changes.

d)  Name 2 strengths and 2 weaknesses of git. (Don't forget to create a
    commit after this answer, see *1c*)
    
    Strengths:
    - git protects you from loosing files
    - collaboration and working together is very easy with git
    
    Weaknesses:
    - Especially in the beginning it can be very complicated to use
    - git dosen't work automatically, you have to explicitly use it
    
    
e)  Knit this exercise sheet. Some new files will automatically be
    generated when knitting the sheet e.g. the HTML page. Ignore these
    files, as we only want to track the source files themselves.

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below:
b)  Push your code to this new repository by copying and executing the
    snippet on github listed under
    `…or push an existing repository from the command line`.
c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.

## Exercise 3: Baby-Names in Munich (3.5 Points)

Download the latest open datasets on given names ("Vornamen") from the
open data repository of the city of Munich for the years `2023` and
`2022`.

```{r}
library(tidyverse)
library(readxl)

```


Link: <https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen>

a)  Download the data for both years and track it in git. For small
    datasets like these adding them to git is not a problem.

b)  Load the data for both years into R. Check the type of the count
    variable ("Anzahl") and look into the data to determine why it is
    not numeric? Fix the problem in an appropriate manner, it is OK if
    some of the counts are inaccurate because of this. Explain your
    solution and the repercussions.
```{r}
Jahr2022 <- read.csv("open_data_portal_2022.csv")
class("Anzahl")

Jahr2023 <- read.csv("vornamen-muenchen-2023.csv")
class("Anzahl") 

Jahr2022$Anzahl[Jahr2022$Anzahl=="4 oder weniger"] <- "2"
Jahr2023$Anzahl[Jahr2023$Anzahl=="4 oder weniger"] <- "2"

Jahr2022$Anzahl <- as.numeric(Jahr2022$Anzahl)
Jahr2023$Anzahl <- as.numeric(Jahr2023$Anzahl)

class(Jahr2022$Anzahl)
class(Jahr2023$Anzahl)
```

Da es die Option "4 oder weniger" gibt. Es gibt 4390 Namen von denen über 4000 
diese Bezeichnung für die Anzahl haben. Da wir nicht wissen, wie die
Verteilung aussieht, würde ich jedem dieser Namen die Anuahl 2 geben, 
da dies in der Mitte von 0,1,2,3,4 liegt. 

c)  Calculate the total number of babies born in Munich in 2022
    and 2023. Which year had the bigger baby-boom?
```{r}
sum(Jahr2022$Anzahl)
sum(Jahr2023$Anzahl)
```
In 2022 there was a bigger baby-boom.  
    

d)  Add a new column `year` to both datasets which holds the correct
    year for each.

```{r}
Jahr2022$year <- 2022
Jahr2023$year <- 2023
```

e)  Combine both datasets into one using `bind_rows()`.

```{r}
j <- bind_rows(Jahr2022, Jahr2023)

```

f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.
```{r}
aggregated_data <- j %>%
  group_by(Vorname) %>%
  summarise(Anzahl = sum(Anzahl)) %>%
  arrange(desc(Anzahl))
  
knitr::kable(head(aggregated_data, n=10), caption = "Top 10 names in 2022 and 2023")
```

## Exercise 4: Open Analysis (4 points)

This exercise is a bit more open-ended. You can choose any dataset from
[Our World in Data](https://ourworldindata.org/) and analyze it, while
determining the research question yourself.

a)  Go to <https://github.com/owid/owid-datasets/tree/master/datasets>
    and choose a dataset that interests you. You can have a look at
    <https://ourworldindata.org/> to gather some inspiration.
b)  Download the dataset and track it in git.
c)  Put the name / title of the dataset and a link to it below.

-   Dataset Name: Electricity mix from BP & EMBER
-   Link: <https://github.com/owid/owid-datasets/blob/master/datasets/Electricity%20mix%20from%20BP%20%26%20EMBER%20(2022)/Electricity%20mix%20from%20BP%20%26%20EMBER%20(2022).csv>

d)  Come up with a (research) question you want to answer with the data
    and briefly explain why you believe this is an interesting question
    within one sentence. It should be a question that can be answered
    with the dataset and using R.
    
How much faster or slower is Germany compared to France in in reducing their carbon
intensity of electricity?
It is an interesting question, because energy represents a major part of carbon
emissions, and reducing the carbon intensity of electricity can have a big impact towards
achieving the climate goals.

e)  Use R to answer your chosen question.

```{r}
electricity <- read.csv("Electricity_mix_from_BP_EMBER.csv")

electricity_gf <- electricity %>% 
  filter(Entity=="Germany" | Entity=="France") %>%
  na.omit() %>%
  janitor::clean_names()

electricity_g <- electricity %>% 
  filter(Entity=="Germany") %>%
  na.omit() %>%
  janitor::clean_names()

electricity_f <- electricity %>% 
  filter(Entity=="France") %>%
  na.omit() %>%
  janitor::clean_names()


model_g <- lm(electricity_g$carbon_intensity_of_electricity_g_co2_k_wh ~ electricity_g$year)
model_f <- lm(electricity_f$carbon_intensity_of_electricity_g_co2_k_wh ~ electricity_f$year)
summary(model_g)
summary(model_f)
```

While France has a lower carbon intensity in total, the regression suggests, that
the value is at a constant level.
Germany has a higher carbon intensity overall, but with every year, the value is on
average -5.9 g CO2/kWh lower.

So now, Germany is worse at producing low carbon energy, but is making progress in reducing
the carbon intensity.
France has a better starting point, but it seems, that there is nearly no progress in 
reducing the value further.



f)  Create a meaningful plot / figure with the dataset. Make sure to
    provide a figure caption (via the chunk options / Rmarkdown) and
    correctly label the figure.
    
```{r figure1, fig.align='left', fig.cap="Carbon intensity Germany and France"}
ggplot(
  data = electricity_gf,
  mapping = aes(
    x = year,
    y = carbon_intensity_of_electricity_g_co2_k_wh,
    color = entity
  )
) + geom_point() +
  labs(
    title = "Carbon intensity of electricity in Germany and France",
    x = "Year",
    y = "Carbon intensity of electricity in  g CO2/kWh",
    color = "Country and linear regression"
) + geom_smooth(method = "lm", se = TRUE)
```


## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
